Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-30 proposal/prop.tex
prop.tex \section{Broader Impact and Education} Add citation...

\noindent (A) {\em Integration of research and education:} Courses on
advanced computational models and quantum information will be further
developed at Indiana University to communicate the basic concepts and
tools discussed in this proposal. Dr. Ortiz taught courses on
``Quantum information and Computation'' and Dr. Sabry has taught
courses on ``Quantum Computing'' for graduate students.  Dr.\ Hanson
has taught courses on scientific visualization and mathematical
modeling with emphasis on high-dimensional mathematics.  His numerous
Siggraph course presentations are embodied in his 2006 book {\it
  Visualizing Quaternions\/}, which remains the definitive treatment
of the subject for computer science and data analysis applications and
has sold thousands of copies. As a part of Dr.\ Hanson's commitment to
exposing and explaining the elements of higher mathematics to the
public, he has recently led the design of a free iPhone App, {\it
  4Dice\/}, that for the first time makes available an interactive
treatment of a correctly imaged simulation of the appearance of a
hypercube, realizing interactively his YouTube animation of the same
name.  This framework is now being generalized for a broad family of
iPhone Apps to permit the hands-on study of high-dimensional
mathematics.  These courses were highly appreciated by the students as
noted by their evaluations in making the material extremely accessible
and interesting.  The PIs plan to engage high school students or
undergraduates in the implementation of some of the ideas.  The PIs
have a long standing commitment to K-12 science and math education
(see also (C) below). The collaborative group efforts will provide
students, as well as the PIs with a unique learning experience. The
broadened perspectives gained through those efforts will contribute to
the PIs effectiveness as teachers and mentors. They also will enable
to better prepare students and postdocs for productive careers in an
increasingly competitive global economy. Students and postdocs are
encouraged to pursue collaborative research leading to a broader
scientific program. This is highlighted by the PIs students' close
contact with LANL, the Perimeter Institute, and the Institute for
Quantum Computing at Waterloo.

>>>>

\noindent (A) {\em Integration of research and education:} Courses on
advanced computational models and quantum information will be further
developed at Indiana University to communicate the basic concepts and
tools discussed in this proposal. Dr. Ortiz taught courses on
``Quantum information and Computation'' and Dr. Sabry has taught
courses on ``Quantum Computing'' for graduate students.  Dr.\ Hanson
has taught courses on scientific visualization and mathematical
modeling with emphasis on high-dimensional mathematics.  His numerous
Siggraph course presentations are embodied in his 2006 book {\it
  Visualizing Quaternions\/}~\cite{Hanson2006}, 
which remains the definitive treatment
of the subject for computer science and data analysis applications and
has sold thousands of copies. As a part of Dr.\ Hanson's commitment to
exposing and explaining the elements of higher mathematics to the
public, he has recently led the design of a free iPhone App, {\it
  4Dice\/}, that for the first time makes available an interactive
treatment of a correctly imaged simulation of the appearance of a
hypercube, realizing interactively his YouTube animation of the same
name.  This framework is now being generalized for a broad family of
iPhone Apps to permit the hands-on study of high-dimensional
mathematics.  These courses were highly appreciated by the students as
noted by their evaluations in making the material extremely accessible
and interesting.  The PIs plan to engage high school students or
undergraduates in the implementation of some of the ideas.  The PIs
have a long standing commitment to K-12 science and math education
(see also (C) below). The collaborative group efforts will provide
students, as well as the PIs with a unique learning experience. The
broadened perspectives gained through those efforts will contribute to
the PIs effectiveness as teachers and mentors. They also will enable
to better prepare students and postdocs for productive careers in an
increasingly competitive global economy. Students and postdocs are
encouraged to pursue collaborative research leading to a broader
scientific program. This is highlighted by the PIs students' close
contact with LANL, the Perimeter Institute, and the Institute for
Quantum Computing at Waterloo.
